---
title: "AirFrance Business Case"
author: 'Team #16'
date: "12/15/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
library(readxl)
library(scales)
library(tidyverse)
library(ggplot2)
library(plotly)
AirFrance_df <- read_excel("AirFrance case.xls")

Final_AirFrance_df <- na.omit(AirFrance_df)

Final_AirFrance_df$`Publisher ID` <- NULL
Final_AirFrance_df$`Keyword ID` <- NULL

Final_AirFrance_df$Net_Rev <- Final_AirFrance_df$Amount - Final_AirFrance_df$`Total Cost`
Final_AirFrance_df$ROA <- Final_AirFrance_df$Net_Rev / Final_AirFrance_df$`Total Cost`
Final_AirFrance_df$Avg_Rev_Booking <- Final_AirFrance_df$Amount / Final_AirFrance_df$`Total Volume of Bookings`
Final_AirFrance_df$Prob_of_Booking <- (Final_AirFrance_df$`Trans. Conv. %` * Final_AirFrance_df$`Engine Click Thru %` /10000)*100
Final_AirFrance_df$Cost_Booking <- Final_AirFrance_df$`Total Cost` / Final_AirFrance_df$`Total Volume of Bookings`

Final_AirFrance_df$`Match Type` <- as.factor(Final_AirFrance_df$`Match Type`)
Final_AirFrance_df$`Bid Strategy` <- as.factor(Final_AirFrance_df$`Bid Strategy`)
Final_AirFrance_df$Status <-as.factor(Final_AirFrance_df$Status)
Final_AirFrance_df$`Publisher Name` <- as.factor(Final_AirFrance_df$`Publisher Name`)
Final_AirFrance_df$`Keyword Group` <- as.factor(Final_AirFrance_df$`Keyword Group`)
Final_AirFrance_df$Category <- as.factor(Final_AirFrance_df$Category)
Final_AirFrance_df$Campaign <- as.factor(Final_AirFrance_df$Campaign)

Final_AirFrance_df$publisher_numeric <- as.numeric(Final_AirFrance_df$`Publisher Name`)
Final_AirFrance_df$match_numeric  <- as.numeric(Final_AirFrance_df$`Match Type`)
Final_AirFrance_df$keyword_group_numeric <- as.numeric(Final_AirFrance_df$`Keyword Group`)
Final_AirFrance_df$campaign_numeric <- as.numeric(Final_AirFrance_df$Campaign)

for(i	in	1:nrow(Final_AirFrance_df)){
  if(Final_AirFrance_df$Prob_of_Booking[i]	=="0"){
    Final_AirFrance_df$Prob_of_Booking[i]	<- 0
  }else{
    Final_AirFrance_df$Prob_of_Booking[i]	<- 1
  }
}

my_normal <- function(x){
  my_min <- min(x, na.rm=TRUE)
  my_max <- max(x, na.rm=TRUE)
  normalized <- (x-my_min)/(my_max-my_min)
  return(normalized)
}

Final_AirFrance_df$ROA_norm <- my_normal(x=Final_AirFrance_df$ROA)
Final_AirFrance_df$Publisher_norm <- my_normal(x=Final_AirFrance_df$publisher_numeric)
Final_AirFrance_df$Campaign_norm <- my_normal(x=Final_AirFrance_df$campaign_numeric)
Final_AirFrance_df$Match_type_norm <- my_normal(x=Final_AirFrance_df$match_numeric)
Final_AirFrance_df$Impressions_norm <- my_normal(x=Final_AirFrance_df$Impressions)
Final_AirFrance_df$Engine_click_norm <- my_normal(x=Final_AirFrance_df$`Engine Click Thru %`)
Final_AirFrance_df$Conversion_norm <- my_normal(x=Final_AirFrance_df$`Trans. Conv. %`)
Final_AirFrance_df$Avg_booking_norm <- my_normal(x=Final_AirFrance_df$Avg_Rev_Booking)
Final_AirFrance_df$Cost_click_norm <- my_normal(x=Final_AirFrance_df$`Avg. Cost per Click`)
Final_AirFrance_df$Avg_pos_norm <- my_normal(x=Final_AirFrance_df$`Avg. Pos.`)
Final_AirFrance_df$click_norm <- my_normal(x=Final_AirFrance_df$Clicks)
Final_AirFrance_df$keyword_group_norm <- my_normal(x=Final_AirFrance_df$keyword_group_numeric)
Final_AirFrance_df$Total_Bookings_norm <- my_normal(x=Final_AirFrance_df$`Total Volume of Bookings`)
Final_AirFrance_df$Revenue_norm <- my_normal(x=Final_AirFrance_df$Net_Rev)
Final_AirFrance_df$Click_Charges_norm <- my_normal(x=Final_AirFrance_df$`Click Charges`)
Final_AirFrance_df$Cost_Booking_norm <- my_normal(x=Final_AirFrance_df$Cost_Booking)
```

## Problem Statement

How to optimize the search engine marketing (SEM) for Air France

## Requirements

- Find the ideal SEM campaign to ensure the optimal amount of sales of tickets
- Selection of appropriate keywords
- Selection of efficient allocation of ad $ through search engines
- Offer strategies for placement on the search results page for Internet Users

## Results of Logistic Regression

```{r logistic, echo = FALSE, include=TRUE, warning=FALSE}
Airfrance_logit <- glm(Prob_of_Booking ~ Campaign_norm + 
                         Impressions_norm + Avg_pos_norm, 
                       data=Final_AirFrance_df,family="binomial")
summary(Airfrance_logit)

library(caret)
library(e1071)

my_prediction <- predict(Airfrance_logit, Final_AirFrance_df, type="response")

confusionMatrix(data=as.factor(as.numeric(my_prediction>0.5)),
                reference=as.factor(as.numeric(Final_AirFrance_df$Prob_of_Booking)))

```

## Plot of the performance of the model


```{r prediction, echo=FALSE, include=TRUE, warning=FALSE}

#We plot the prediction model
library(ROCR)

pred_val_logit <- prediction(my_prediction, Final_AirFrance_df$Prob_of_Booking)

#Runs the confusion matrices for different values of p(p=0-1). Sensitivity analysis
perf_logit <- performance(pred_val_logit, "tpr", "fpr")

plot(perf_logit, col="blue")
```

## Decision Tree

``` {r decision tree, echo=FALSE, include=TRUE, warning=FALSE}
library(rpart)
library(rpart.plot)
my_Airfrance_tree <- rpart(Prob_of_Booking ~ Campaign_norm + Impressions_norm + Avg_pos_norm,
                      data=Final_AirFrance_df,
                      method="class", cp=0.01)

rpart.plot(my_Airfrance_tree, type=1, extra=1,
           box.palette = c("red", "turquoise"),
           branch.lty=3, shadow.col = "gray")

```

## Plot Investment for each Publisher

```{r sum data, echo=FALSE, include=FALSE, warning=FALSE}

sum_data_Airfrance <- Final_AirFrance_df %>% group_by(`Publisher Name`) %>% summarise(Total_Bookings=sum(`Total Volume of Bookings`), Revenue=sum(Net_Rev),
                                                                                      Click_Charges=sum(`Click Charges`), roa=sum(ROA), Prob_Booking=sum(Prob_of_Booking),
                                                                                      Cost_Book=sum(Cost_Booking), Cost_click=sum(`Avg. Cost per Click`), Rev_Booking=sum(Avg_Rev_Booking),
                                                                                      Click_rate=sum(`Engine Click Thru %`), Conversion_rate=sum(`Trans. Conv. %`),na.rm=TRUE)

```
```{r plot, echo=FALSE, include=TRUE, warning=FALSE}
library(ggplot2)
plot1 <- plot_ly(type = "scatter",
                 sum_data_Airfrance, 
                 x = ~sum_data_Airfrance$Prob_Booking, 
                 y = ~sum_data_Airfrance$Cost_click,
                 text = ~paste("Publisher: ", rownames(sum_data_Airfrance)),
                 mode = "markers",
                 size = sum_data_Airfrance$Prob_Booking,
                 sizes = c(10,100), # Change to make bubbles bigger
                 marker = list(opacity = 1, sizemode = "diameter"),
                 color = ~sum_data_Airfrance$`Publisher Name`)

plot1 <- plot1 %>% layout(title = "Investment per Publisher",
                          xaxis = list(title = "Probability of Booking per Publisher",
                                       gridcolor = "light grey"),
                          yaxis = list(title = "Average Cost per Click per Publisher",
                                       gridcolor = "light grey"),
                          showlegend = TRUE,
                          paper_bgcolor = "white",
                          plot_bgcolor = "white")

plot1
```

## Plot Efficiency of each Publisher


```{r plot2, echo=FALSE, include=TRUE, warning=FALSE}
library(ggplot2)
plot2 <- plot_ly(type = "scatter",
                 sum_data_Airfrance, 
                 x = ~sum_data_Airfrance$Click_rate, 
                 y = ~sum_data_Airfrance$Conversion_rate,
                 text = ~paste("Publisher: ", rownames(sum_data_Airfrance)),
                 mode = "markers",
                 size = sum_data_Airfrance$Click_rate,
                 sizes = c(10,100), # Change to make bubbles bigger
                 marker = list(opacity = 1, sizemode = "diameter"),
                 color = ~sum_data_Airfrance$`Publisher Name`)

plot2 <- plot2 %>% layout(title = "Efficiency of each Publisher",
                          xaxis = list(title = "Click thru Rate",
                                       gridcolor = "light grey"),
                          yaxis = list(title = "Conversion Rate",
                                       gridcolor = "light grey"),
                          showlegend = TRUE,
                          paper_bgcolor = "white",
                          plot_bgcolor = "white")

plot2
```


## Plot Impressions

```{r plot3, echo=FALSE, include=TRUE, warning=FALSE}

Final_AirFrance_df$`Impressions/Booking` <- round(log(Final_AirFrance_df$`Impressions` / Final_AirFrance_df$`Total Volume of Bookings`), digits = 2)

ggplot(Final_AirFrance_df,aes(x=Final_AirFrance_df$`Publisher Name`, y= Final_AirFrance_df$`Impressions/Booking`,fill=Final_AirFrance_df$`Publisher Name`)) + 
  geom_boxplot() 

```



## Plot Campaign


```{r plot4, echo=FALSE, include=TRUE, warning=FALSE}
Final_AirFrance_df$`Impressions/Booking_log` <- round(log(Final_AirFrance_df$`Impressions` / Final_AirFrance_df$`Total Volume of Bookings`), digits = 2)
ggplot(Final_AirFrance_df,aes(x=`Campaign`, y= `Impressions/Booking_log`,fill=`Campaign`)) + 
  geom_boxplot() +
  geom_hline(yintercept=7, linetype="dashed", color = "red") +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

```


## Plot Match Type


```{r plot 5, echo=FALSE, include=TRUE, warning=FALSE}
x <- ggplot(Final_AirFrance_df, aes(x=`Publisher Name`, y=`Trans. Conv. %`, group=`Match Type`)) +
  geom_point(aes(color=`Match Type`, size=`Match Type`), alpha=0.4)
ggplotly(x)
```

## Plot Revenue Comparison - Publishers vs Kayak

```{r Kayak, echo=FALSE, include=TRUE, warning=FALSE}
Kayak_Airfrance_Revenue <- ggplot() +
  geom_point(data=sum_data_Airfrance, aes(x=`Publisher Name`, y=`Revenue`), color="blue") +
  geom_point(data= NULL, aes(x="Kayak", y=230126.86), color="orange") +
  geom_hline(yintercept = mean(sum_data_Airfrance$Revenue), color="red")

ggplotly(Kayak_Airfrance_Revenue)
```

## Plot Booking comparison - Publishers vs Kayak

```{r plot kayak2, echo=FALSE, include=TRUE, warning=FALSE}

Kayak_Airfrance_Bookings <- ggplot() +
  geom_point(data=sum_data_Airfrance, aes(x=`Publisher Name`, y=`Total_Bookings`), color="blue") +
  geom_point(data= NULL, aes(x="Kayak", y=208), color="orange") +
  geom_hline(yintercept = mean(sum_data_Airfrance$Total_Bookings), color="red")

ggplotly(Kayak_Airfrance_Bookings)

```

## Conclusions & Recommendations

-Reduce Ad spending budget on Yahoo & MSN

-Invest more in metasearch websites like Kayak

-Focus on the high performing campaigns like Air France Global & Western Europe destinations, reduce geo-targeted US cities campaigns

-Broad keyword match type results in higher transaction conversion percentage











